Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.5 Numeric representations and soundness

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\subsection{Fixed word length effects on matrix multiplications}
%\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model. Thus any mathematical operations occurring in the digital controller will occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.

>>>>

We use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model. Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations are carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
